### 2021-05-11 article/article.tex
update

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.35\linewidth]{figures/cascade_flux_ratio.pdf}
      \hspace{1.5cm}
      \includegraphics[width=0.35\linewidth]{figures/track_flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}
\end{figure}%Done, run code in nsi.ipynb. need high emt and log to show both cascade and track features at the same time.
%otherwise, the cascade ratio overpowers the track one.

@@

\begin{figure}[!tb]
   \begin{center}
      \begin{subfigure}{0.45\textwidth}
         \includegraphics[width=1\linewidth]{figures/joint_3D_NO.pdf}
         \caption{Normal ordering}\label{fig:joint_3D}
      \end{subfigure}
      \hspace{0cm}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
         \caption{DeepCore}\label{fig:DC_3D_NO}
      \end{subfigure}
    \end{center}
    \caption{Expected $\Delta \chi^2$ after three years of data.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
 \end{figure}
%TODO:explain emt assymetry. dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
%TODO: ploit contour for ett-emt
 \begin{table}
   \begin{center}
   \begin{tabular}{lcc}
           \hline \hline \\
           Parameter & 90\% CL & $3\sigma$  \\
           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
\end{table}

>>>>

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}
\end{figure}%TODO:redo with more than 100x100. need high emt and log to show both cascade and track features at the same time.
%otherwise, the cascade ratio overpowers the track one.

@@

\begin{figure}[!tb]
   \begin{center}
      \begin{subfigure}{0.45\textwidth}
         \includegraphics[width=1\linewidth]{figures/joint_3D_NO.pdf}
         \caption{Normal ordering}\label{fig:joint_3D}
      \end{subfigure}
    \end{center}
    \caption{Expected $\Delta \chi^2$ after three years of data.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
 \end{figure}
%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?

% \begin{figure}[!tb]%TODO: redo this with P+/P-
% \begin{center}
%    \includegraphics[width=0.7\linewidth]{figures/Pmm_asymmetry.pdf}
% \end{center}
% \caption{Expected $\Delta \chi^2$ after three years of data.
%    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
%    parameters other than the one shown in each panel are fixed to zero.}\label{fig:Pmm_asymmetry}
% \end{figure}

We can explain the asymmetry by looking looking at the oscillogram of the ratio $P(\emt^-)/P(\emt^+)$ in Fig.~\ref{fig:Pmm_asymmetry}, which is the $P_{\mu\mu}$ survival probability
given $\emt =-0.05$ divided by $P_{\mu\mu}$ for $\emt=0.05$. Muon events are the most abundant in IceCube and DeepCore/PINGU, and it suffices to study
$P_{\mu\mu}$ to explain the asymmetry. We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (pink area),
while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in the flux ratio plot, this muon survival abundance 
is indeed preserved at flux level.

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.5\linewidth]{figures/emt_events.pdf}
   \end{center}
   \caption{The best-fit event count ratio at each detector for negative and positive $\emt$. PINGU shows promising 
   of distinguishing the sign of $\emt$, but favoring $\emt < 0$ while DeepCore has higher statistics for $\emt>0$ and a poor
   distinction for $\emt<0$}\label{fig:emt_events}%TODO: improve caption?
 \end{figure}
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event count for $\emt=-0.02$ outnumber the event count with $\emt =0.05$ for
all bins except one, giving a high $\Delta \chi^2$ on both sides and slightly higher for $\emt=-0.02$. DeepCore on the other hand, 
has no bins where the event count for $\emt=-0.02$ surpasses the event count for $\emt=+0.02$, giving weak statistics for the negative side.

%TODO: ploit contour for ett-emt
 \begin{table}
   \begin{center}
   \begin{tabular}{lcc}
           \hline \hline \\
           Parameter & 90\% CL & $3\sigma$  \\
           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
\end{table}
